Parameter estimation

### 2023-03-10 SFE-article/Sections/Results.tex
10.03

>>>>

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.7\textwidth}
		\centering
		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T40_P200_F0.41_No_Delay}
		\caption{Experiment at $40^\circ C$ and $200$ bar}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.7\textwidth}
		\centering
		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T50_P200_F0.41_No_Delay.pdf}
		\caption{Experiment at $50^\circ C$ and $200$ bar}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.7\textwidth}
		\centering
		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T40_P300_F0.41_No_Delay.pdf}
		\caption{Experiment at $40^\circ C$ and $300$ bar}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.7\textwidth}
		\centering
		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T50_P300_F0.41_No_Delay.pdf}
		\caption{Experiment at $50^\circ C$ and $300$ bar}
	\end{subfigure}
	\caption{Results of parameter fitting, with estimation of the initial state}
\end{figure*}
